Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-31 draft/paper1_jenny.tex
Edit SMF

@@

@@

@@

    Overall, this illustrates again that our 1-D approach has certain advantages 
    over the 2-D modeling method and in principle, should capture the majority of 
    the total \mstar{}.

    For studies about the SMF or other aspects of galaxy evolution based on 
    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
%% ------------------------------------------------------------------------------------ %% 
    It is clear that different analyses lead to very different slopes at high-mass end. 
    Here, we do not try to evaluate whether the differences displayed in 
    Fig~\ref{fig:smf} are dominated by differences in photometry versus 
    assumptions about stellar population models (e.g. \citealt{Bernardi2017}). 
    However, given that the results that we are comparing assume the same IMF and adopt 
    similar assumptions about stellar population models, we hypothesize that the 
    differences in Fig~\ref{fig:smf} are dominated by differences in photometry. 
    The goal of our of present paper is not to present and discuss a careful evaluation
    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
    once the HSC survey has accumulated more data. 
    However, this is clearly a topic that warrants further investigation, and careful 
    photometry measurements from HSC data will shed further light on these questions.

@@

    Meanwhile, \mstar{} measurement based on SED fitting heavily depends on the 
    adopted SSP model, the form of IMF, dust extinction law, and details in 
    the assumption of SFH (e.g.\ \citealt{Bernardi2016b}). 
    For massive galaxies in this sample, the form of the SFH\footnote{We choose 
    to use the delayed-$\tau$ model for SFH; we adopt flat distribution between 
    0.5 to 14.0 Gyrs as the prior for the look-back time when the star formation 
    turned on. 
    The exponential delayed time-scale ($\tau$) is allowed to change between 
    0.1 to 3.0 with equal probability}, the contribution from random star 
    burst\footnote{The chance of random star burst is set at 0.2 for every 2 Gyrs. 
    The duration of the star burst is draw from a logarithmic distribution 
    between 0.03 to 0.3 Gyr; and the mass fraction formed in the burst is from 
    a logarithmic distribution between 0.01 and 1.0.} rarely affect the \mstar{}. 
    But he choices of SSP model, IMF, and dust extinction do systematically impact
    the estimates of \mstar{}, and therefore we look into this with a few 
    additional tests (see Fig~\ref{fig:ised_3}):

>>>>

    On the same figure, we also compare the HSC results with the ones from following 
    works:

@@

        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
            \citep{Leauthaud2016} where the \mstar{} is derived using 
            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
            \texttt{S82}.
            The stellar population model and star-formation history assumptions are 
            very similar to the ones in this work, except that it uses the 
            \texttt{BC03} model. 
            Based on the test results from Appendix \ref{app:sed}, we simply shifts 
            the SMF to higher \mstar{} by 0.08 dex.

@@

        \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from 
            \citet{Bernardi2017}. 
            The total luminosity is based on 2-D \texttt{SerExp} models 
            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
            recovers much more flux compared to SDSS \cmodel{} magnitudes 
            (\citealt{Bernardi2013, Meert2015}). 
            The \m2l{} is adopted from the SED fitting results from the ``dusty'' 
            model in \citet{Mendel2014} which share similar assumptions of stellar 
            population models with this work.

@@

    To appropriately compare SMFs from different works, one needs to carefully 
    separate the differences in the measurements of luminosity and \m2l{}, and 
    takes the uncertainties of \mstar{} measurements into account\footnote{
    Fixed uncertainty of \logms{} can lead to increasingly over-estimated 
    volume density with \mstar{} due to the very steep slope of SMF at high-mass end.} 
    (\citealt{Bernardi2010, Bernardi2017}), which is beyond the scope of this work.  
    Here, we primarily want to visualize the importance of \mstar{} measurements 
    to the SMF at high-mass end. 
    All SMFs share similar volume density around \logms{}${\sim}11.0$, but the ones
    that are based on \texttt{cModel} and small aperture photometry show much 
    steeper slopes than the HSC \mtot{} one. 
    The SMF based on single-\ser{} model seems to face the same issue. 
    We also compare with the $z{\sim}0.1$ SMF from the GAMA survey 
    (\citealt{Wright2017}) whose luminosity is scaled with the single-\ser{} model
    from \citet{Kelvin2012}, and its high-mass end behavior is very similar to 
    the \citet{Leauthaud2016} and the \citet{Moustakas13} ones. 
    And, once the \m2l{} measurements based on similar assumptions are adopted, 
    the SDSS SMF using the \texttt{SerExp} models from \citet{Bernardi2017} becomes 
    surprisingly similar to the HSC \mtot{} one that is not model dependent.
    Both SMFs highlight the importance of ``missing light'' from different angles. 
    Right now, the \citet{Bernardi2017} sample and our HSC one have almost no 
    galaxy in common due to the differences in redshift range, hence it is not 
    clear whether the \texttt{SerExp} model can indeed describe the flux 
    distributions of these massive galaxies out to $>100$ kpc. 
    It would be interesting to look into the application of multi-component 
    2-D models using HSC images.

    In summary, the result highlights that the SMF at high-mass end is sensitive to 
    even moderate change of \mstar{}, and illustrates the advantages of deep HSC image
    and careful 1-D approach in estimating total \mstar{} of massive galaxies.
    For studies about the SMF or other aspects of galaxy evolution based on 
    shallow image or simplified model, these effects can not be neglected.
    Although we only discuss the high-mass end, this \mstar{} range is crucial for 
    tracing the evolution of massive galaxies and calibrating numerical simulation 
    and semi-analytic model as it is very sensitive to the AGN-feedback recipe.   
%% ------------------------------------------------------------------------------------ %%

@@

    Meanwhile, \mstar{} measurement based on SED fitting heavily depends on the 
    adopted SSP model, the form of IMF, dust extinction law, and details in 
    the assumption of SFH (e.g.\ \citealt{Bernardi2017}). 
    For massive galaxies in this sample, the form of the SFH\footnote{We choose 
    to use the delayed-$\tau$ model for SFH; we adopt flat distribution between 
    0.5 to 14.0 Gyrs as the prior for the look-back time when the star formation 
    turned on. 
    The exponential delayed time-scale ($\tau$) is allowed to change between 
    0.1 to 3.0 with equal probability}, the contribution from random star 
    burst\footnote{The chance of random star burst is set at 0.2 for every 2 Gyrs. 
    The duration of the star burst is draw from a logarithmic distribution 
    between 0.03 to 0.3 Gyr; and the mass fraction formed in the burst is from 
    a logarithmic distribution between 0.01 and 1.0.} rarely affect the \mstar{}. 
    But he choices of SSP model, IMF, and dust extinction do systematically impact
    the estimates of \mstar{}, and therefore we look into this with a few 
    additional tests (see Fig~\ref{fig:ised_3}):
